Probabilistic Catalogs from Crowded Star Fields

### 2012-07-24 paper/ms.tex
Change in notation
Doing integrals
Parameters

\section{Broken Pareto Distribution}
The Broken Pareto distribution is:
\begin{eqnarray}
p(x | \theta) &\propto&
\left\{
\begin{array}{lcr}
0, & & x < x_0 \\
x^{-\alpha_1 - 1}, & & x_0 \leq x \leq x_1 \\
x^{-\alpha_2 - 1}, & & x > x_1
\end{array}
\right.
\end{eqnarray}
We will need the fully normalised version. Putting in two normalising constants:
\begin{eqnarray}
p(x | \theta) &=&
\left\{
\begin{array}{lcr}
0, & & x < x_0 \\
C_1x^{-\alpha_1 - 1}, & & x_0 \leq x \leq x_1 \\
C_2x^{-\alpha_2 - 1}, & & x > x_1
\end{array}
\right.
\end{eqnarray}
The normalising constants can be obtained by enforcing the following
constraints. The first constraint is that the total probability is unity:
\begin{eqnarray}
\int p(x|\theta) \, dx = 1
\end{eqnarray}
The second constraint is that the PDF should be continuous at $x=x_1$:
\begin{eqnarray}
C_1 x_1^{-\alpha_1 - 1} = C_2 x_1^{-\alpha_2 - 1}
\end{eqnarray}

>>>>

\section{Broken Pareto Distribution}
The Broken Pareto distribution is:
\begin{eqnarray}
p(x | \theta) &\propto&
\left\{
\begin{array}{lcr}
0, & & x < x_0 \\
x^{-\alpha_1 - 1}, & & x_0 \leq x \leq x_1 \\
x^{-\alpha_2 - 1}, & & x > x_1
\end{array}
\right.
\end{eqnarray}
where the parameters are $\theta = \{x_0, x_1, \alpha_0, \alpha_1\}$.
We will need the fully normalised version. Putting in two normalisers:
\begin{eqnarray}
p(x | \theta) &=&
\left\{
\begin{array}{lcr}
0, & & x < x_0 \\
Z_1^{-1}x^{-\alpha_1 - 1}, & & x_0 \leq x \leq x_1 \\
Z_2^{-1}x^{-\alpha_2 - 1}, & & x > x_1
\end{array}
\right.
\end{eqnarray}
The normalising constants can be obtained by enforcing the following
constraints. The first constraint is that the PDF should be continuous at
$x=x_1$:
\begin{eqnarray}
Z_1^{-1} x_1^{-\alpha_1 - 1} &=& Z_2^{-1} x_1^{-\alpha_2 - 1} \\
\implies Z_2 &=& Z_1 x_1^{\alpha_1-\alpha_2}
\end{eqnarray}
The second constraint is that the total probability is unity:
\begin{eqnarray}
\int p(x|\theta) \, dx &=& 1 \\
\implies
Z_1 &=& 
\int_{x_0}^{x_1} x^{-\alpha_1 - 1} \, dx
+ x_1^{\alpha_2-\alpha_1} \int_{x_1}^\infty x^{-\alpha_2 - 1}\, dx \\
&=& \left[-\frac{x^{-\alpha_1}}{\alpha_1}\right]_{x_0}^{x_1}
+ x_1^{\alpha_2-\alpha_1}\left[-\frac{x^{-\alpha_2}}{\alpha_2}\right]_{x_1}^\infty \\
&=& \frac{x_0^{-\alpha_1} - x_1^{-\alpha_1}}{\alpha_1}
+ \frac{x_1^{-\alpha_1-\alpha_2}}{\alpha_2}
\end{eqnarray}
